The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-15 document/ms.tex

In order to predict how many EBs or BEBs we might expect to detect in this 
particular search of \kepler\ data, we first need to choose reasonable parameters
for the binary star population.  To do this, we calibrate the population 
parameters using the catalog of detected \kepler\ eclipsing binaries.  We
find that a binary fraction of 15\% between periods of 20 days and 25 years, with
periods distributed as $f(P) \sim P^{-1.1}$ and eccentrities distributed according
to $\beta(0.8, 2.0)$ is able to reproduce well both the number and period 
distribution of

The \kepler\
EB catalog contains 698 EBs with periods between 20 and 1000 days

The first step in determining EBs and BEBs

>>>>

In order to predict how many EBs or BEBs we might expect to detect in this 
particular search of \kepler\ data, we first need to choose reasonable parameters
for the binary star population.  To do this, we calibrate the population 
parameters using the catalog of detected \kepler\ eclipsing binaries.  We
find that a binary fraction of 15\% between periods of 20 days and 25 years, with
periods distributed as $f(P) \sim P^{-1.1}$ and eccentrities distributed according
to $\beta(0.8, 2.0)$ is able to reproduce well both the number and period 
distribution of observed \kepler\ EBs between 20 and 1000 days.  We thus fix these
binary star population parameters for our subsequent EB and BEB simulations.
